Verifying Demonstrations

### 2018-08-30 paper/DB-anon-cred.tex
Adds description of DB-Schnorr (WIP #133)

We present the protocol in \cref{SchnorrFigure}.
The main difference to the original Schnorr protocol is that the prover commits 
to one random value but the verifier sends \emph{two challenges}.
This is also different from Brands-Chaum, where the prover and verifier jointly 
construct the challenge.
(We let \(|q| = \ceil{\log_2 q}\) denote the length of \(q\) in bits.)
The verifier will request all \(|q|\) response-bits from one challenge and only 
\(l > 0\) from the other.
The prover must know the responses for both challenges to successfully pass the 
\ac{DB} phase.
The reason for the two challenges (change from Schnorr) is that
knowing the responses to both means learning $\alpha$ (for
\ac{DBTF}). Bundling the authentication into the distance bounding
phase (additional change from Brands-Chaum) was done for \ac{DBDH},
and both adaptations together aim at \ac{DBMF} resistance. %reducing success of MF according to number of repetitions.

@@

    % null
    &
    & Construct \(r = s_b\) as the concatenation of \(r_i\)'s for which \(b_i = 
      b\).
      Accept if \(R = g^r A^{c_b}\).
    \\

>>>>

We present the protocol in \cref{SchnorrFigure}.
The group with generator \(g\) and order \(q\) are system parameters.
The private key \(\alpha\) with public key \(A = g^\alpha\) are generated once 
by the prover in the setup phase.

During one round, the prover generates a random nonce \(\rho\rgets \ZZ_q\), 
computes \(R\gets g^\rho\) and sends \(R\) to the verifier.
The verifier generates two challenges \(c_0\rgets \bin^k, c_1\rgets \bin^k\) 
and sends them to the prover.
The prover computes \(s_0\gets \rho - c_0\alpha, s_1\gets \rho - c_1\alpha\).
This is the main difference to the original Schnorr protocol: the verifier 
selects two challenges and the prover \emph{computes} two responses --- but 
still only \emph{one nonce}, \(\rho\).
(This is also different from Brands-Chaum, where the prover and verifier 
jointly construct \emph{one} challenge with \emph{one} response.)
We let \(|q| = \ceil{\log_2 q}\) denote the length of \(q\) in bits.
The verifier will request all \(|q|\) response-bits from one challenge (say 
\(s_b, b\in \bin\)) and only \(l > 0\) from the other (\(s_{1-b}\)).
Finally, the verifier has \(s_b\) and can authenticate the prover by checking 
if \(R = g^{s_b}A^{c_b}\).

The prover must know the responses for both challenges to successfully pass the 
\ac{DB} phase.
The reason for the two challenges but only one random nonce (change from 
Schnorr) is that knowing the responses to both means learning \(\alpha\) (for
\ac{DBTF}).
Bundling the authentication into the distance bounding phase (difference from 
Brands-Chaum) was done for \ac{DBDH},
and both adaptations together aim at \ac{DBMF} resistance. %reducing success of MF according to number of repetitions.

@@

    % null
    &
    & Construct \(s_b\) as the concatenation of \(r_i\)'s for which \(b_i = 
      b\).
      Accept if \(R = g^{s_b} A^{c_b}\).
    \\
